---
title: "test"
author: "Jie Chen"
date: "`r Sys.Date()`"
output: pdf_document
---

## 1. Test varyQ and original ALS with equal Q

```{r}
library("mclust")
library("multichull")
source("./functions/data_simulation_functions.R")
source("./functions/ClusterwiseJICA_varyQ.R")
source("./functions/ClusterwiseJICA.R")
source("./functions/CJICA_asist_functions.R")
source("./functions/ILS_CJICA.R")
```

```{r}
# generate simulation data
set.seed(123)
test_data <- Simulate_CJICA(Nk = 10, Vm = 2500, K = 4, Qvect = c(5, 5, 5, 5), E = .1, M = 2, type = 1, cor = .05, VAF = 1)
str(test_data)
```

```{r}
# original value
set.seed(123)
original_result <- ClusterwiseJICA(X = test_data$Xe, k = 4, nc = 5, starts = 100, scale = T)
originalARI <- adjustedRandIndex(test_data$P, original_result[[length(original_result)]]$p)
```

```{r}
# change to vector value, with fixed Q
set.seed(123)
ncVector_result <- ClusterwiseJICA_varyQ(X = test_data$Xe, k = 4, nc = c(5, 5, 5, 5), fixQ = T, starts = 100, scale = T)
ncVectorlARI <- adjustedRandIndex(test_data$P, ncVector_result[[length(ncVector_result)]]$p)
```

```{r}
values <- c(originalARI, ncVectorlARI)
names(values) <- c("originalARI", "ncVectorlARI")
print(values)
```

## 2. Compare ALS and ILS

```{r}
set.seed(123)
ILS_result <- ILS_CJICA(X = test_data$Xe, k = 4, nc = 5, scale = T, iter = 100, stepsize = 1, titlevec = test_data$P, rational = test_data$P)
```

## 3. Compare ALS and PCAALS

```{r}
# compare with nc = 5555
set.seed(123)
pca_result <- ClusterwiseJICA_varyQ(X = test_data$Xe, k = 4, fixQ = F, threshold = 0.8, starts = 100, scale = T)
table(pca_result[[length(pca_result)]]$p)
pcaARI <- adjustedRandIndex(test_data$P, pca_result[[length(pca_result)]]$p)
```

### nc = c(2, 2, 4), Nk = 50

```{r}
# regenerate data with nc = (2, 2, 4)
set.seed(123)
test_data224 <- Simulate_CJICA(Nk = 50, Vm = 2500, K = 3, Qm = c(2, 2, 4), E = .1, M = 2, type = 1, cor = .05)
str(test_data224)
```

```{r}
# original ALS
set.seed(123)
starts <- seq(10, 50, by = 5)
als224ARI <- NULL
for (start in starts) {
  print(start)
  als224_result <- ClusterwiseJICA_varyQ(
    X = test_data224$Xe, k = 3, nc = c(2, 2, 4), fixQ = T,
    starts = start, scale = T
  )
  ARI <- adjustedRandIndex(test_data224$P, als224_result[[length(als224_result)]]$p)
  als224ARI <- append(als224ARI, ARI)
}
```

```{r}
plot(x = starts, y = als224ARI)
```

```{r}
# pca ALS
set.seed(123)
starts <- seq(10, 50, by = 5)
pca224ARI <- NULL
for (start in starts) {
  print(start)
  pca224_result <- ClusterwiseJICA_varyQ(
    X = test_data224$Xe, k = 3, fixQ = F, threshold = 0.8,
    starts = start, scale = T
  )
  ARI <- adjustedRandIndex(test_data224$P, pca224_result[[length(pca224_result)]]$p)
  pca224ARI <- append(pca224ARI, ARI)
}
```

```{r}
plot(x = starts, y = pca224ARI)
```

```{r}
source("./functions/data_simulation_functions.R")
set.seed(123)
test_data <- Simulate_CJICA(Nk = 10, Vm = 2500, K = 4, Qm = c(5, 5, 5, 5), E = .1, M = 2, type = 1, cor = .05)
```

## 4. check new simulation function

```{r}
source("./functions/data_simulation_functions.R")
set.seed(123)
Qvect <- c(2, 3, 4, 5)
test_vaf08 <- Simulate_CJICA(Nk = 10, Vm = 2500, K = 4, Qvect = Qvect, E = .1, M = 2, type = 1, cor = .05, VAF = 1)
```

```{r}
# check the simulation function
vaf <- c()
K <- 4
for (i in 1:K) {
  v <- ssq(test_vaf08$S[[i]][, 1:Qvect[i]] %*% t(test_vaf08$A[[i]][, 1:Qvect[i]])) / ssq(test_vaf08$S[[i]] %*% t(test_vaf08$A[[i]]))
  vaf <- c(vaf, v)
}
vaf
```

## 5. multiple comparition of two model

### vaf = 1, equal Q

1.bad model

```{r}
source("./functions/data_simulation_functions.R")
set.seed(123)
data_Nk50_K5_Q66666_E4_VAF1 <- Simulate_CJICA(Nk = 50, Vm = 2500, K = 5, Qvect = c(6,6,6,6,6), E = .4, M = 2, type = 1, cor = .05, VAF = 1)
save(data_Nk50_K5_Q66666_E4_VAF1, file = "./data/data_Nk50_K5_Q66666_E4_VAF1.RData")
```

```{r}
load("./data/data_Nk50_K5_Q66666_E4_VAF1.RData")

data_Nk50_K5_Q66666_E4_VAF1_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q66666_E4_VAF1$Xe, k = 5, nc = c(6,6,6,6,6), useInputQ = T, starts = 20, scale = T)
save(data_Nk50_K5_Q66666_E4_VAF1_result, file = "./data/data_Nk50_K5_Q66666_E4_VAF1_result.RData")

```

```{r}
loss1 <- sapply(seq_along(data_Nk50_K5_Q66666_E4_VAF1_result), function(anom) tail(data_Nk50_K5_Q66666_E4_VAF1_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk50_K5_Q66666_E4_VAF1_result[[which.min(loss1)]]
data_Nk50_K5_Q66666_E4_VAF1_ARI <- adjustedRandIndex(data_Nk50_K5_Q66666_E4_VAF1$P, optimal$p)
```

2.good model

```{r}
set.seed(123)
data_Nk100_K3_Q444_E02_VAF1 <- Simulate_CJICA(Nk = 100, Vm = 2500, K = 3, Qvect = c(4,4,4), E = .2, M = 2, type = 1, cor = .05, VAF = 1)
save(data_Nk100_K3_Q444_E02_VAF1, file = "./data/data_Nk100_K3_Q444_E02_VAF1.RData")
```

```{r}
data_Nk100_K3_Q444_E02_VAF1_result <- ClusterwiseJICA_varyQ(X = data_Nk100_K3_Q444_E02_VAF1$Xe, k = 3, nc = c(4,4,4), useInputQ = T, starts = 20, scale = T)
save(data_Nk100_K3_Q444_E02_VAF1_result, file = "./data/data_Nk100_K3_Q444_E02_VAF1_result.RData")
```

```{r}
loss2 <- sapply(seq_along(data_Nk100_K3_Q444_E02_VAF1_result), function(anom) tail(data_Nk100_K3_Q444_E02_VAF1_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk100_K3_Q444_E02_VAF1_result[[which.min(loss2)]]
data_Nk100_K3_Q444_E02_VAF1_ARI <- adjustedRandIndex(data_Nk100_K3_Q444_E02_VAF1$P, optimal$p)
```

Compare

```{r}
values <- c(data_Nk50_K5_Q66666_E4_VAF1_ARI, data_Nk100_K3_Q444_E02_VAF1_ARI)
names(values) <- c("badARI", "goodARI")
print(values)
```

### vaf = 0.8, equal Q

1.bad model

```{r}
source("./functions/data_simulation_functions.R")
set.seed(123)
data_Nk50_K5_Q66666_E4_VAF08 <- Simulate_CJICA(Nk = 50, Vm = 2500, K = 5, Qvect = c(6,6,6,6,6), E = .4, M = 2, type = 1, cor = .05, VAF = 0.8)
save(data_Nk50_K5_Q66666_E4_VAF08, file = "./data/data_Nk50_K5_Q66666_E4_VAF08.RData")
```

use vaf = 1

```{r}
load("./data/data_Nk50_K5_Q66666_E4_VAF08.RData")
data_Nk50_K5_Q66666_E4_VAF08_VAF1_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q66666_E4_VAF08$Xe, k = 5, nc = c(6,6,6,6,6), useInputQ = T, starts = 20, scale = T, VAF = 1)
save(data_Nk50_K5_Q66666_E4_VAF08_VAF1_result, file = "./data/data_Nk50_K5_Q66666_E4_VAF08_VAF1_result.RData")

load("./data/data_Nk50_K5_Q66666_E4_VAF08_VAF1_result.RData")
loss1 <- sapply(seq_along(data_Nk50_K5_Q66666_E4_VAF08_VAF1_result), function(anom) tail(data_Nk50_K5_Q66666_E4_VAF08_VAF1_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk50_K5_Q66666_E4_VAF08_VAF1_result[[which.min(loss1)]]
data_Nk50_K5_Q66666_E4_VAF08_VAF1_ARI <- adjustedRandIndex(data_Nk50_K5_Q66666_E4_VAF08$P, optimal$p)
```

use vaf = 0.8

```{r}
data_Nk50_K5_Q66666_E4_VAF08_VAF08_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q66666_E4_VAF08$Xe, k = 5, nc = c(6,6,6,6,6), useInputQ = T, starts = 20, scale = T, VAF = 0.8)
save(data_Nk50_K5_Q66666_E4_VAF08_VAF08_result, file = "./data/data_Nk50_K5_Q66666_E4_VAF08_VAF08_result.RData")

load("./data/data_Nk50_K5_Q66666_E4_VAF08_VAF08_result.RData")
loss1 <- sapply(seq_along(data_Nk50_K5_Q66666_E4_VAF08_VAF08_result), function(anom) tail(data_Nk50_K5_Q66666_E4_VAF08_VAF08_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk50_K5_Q66666_E4_VAF08_VAF08_result[[which.min(loss1)]]
data_Nk50_K5_Q66666_E4_VAF08_VAF08_ARI <- adjustedRandIndex(data_Nk50_K5_Q66666_E4_VAF08$P, optimal$p)
```

```{r}
values <- c(data_Nk50_K5_Q66666_E4_VAF08_VAF1_ARI, data_Nk50_K5_Q66666_E4_VAF08_VAF08_ARI)
names(values) <- c("vaf1ARI", "vaf08ARI")
print(values)
```

2.good model

```{r}
set.seed(123)
data_Nk100_K3_Q444_E02_VAF08 <- Simulate_CJICA(Nk = 100, Vm = 2500, K = 3, Qvect = c(4,4,4), E = .2, M = 2, type = 1, cor = .05, VAF = 0.8)
save(data_Nk100_K3_Q444_E02_VAF08, file = "./data/data_Nk100_K3_Q444_E02_VAF08.RData")
```

use vaf = 1

```{r}
load("./data/data_Nk100_K3_Q444_E02_VAF08.RData")
data_Nk100_K3_Q444_E02_VAF08_VAF1_result <- ClusterwiseJICA_varyQ(X = data_Nk100_K3_Q444_E02_VAF08$Xe, k = 3, nc = c(4,4,4), useInputQ = T, starts = 20, scale = T, VAF = 1)
save(data_Nk100_K3_Q444_E02_VAF08_VAF1_result, file = "./data/data_Nk100_K3_Q444_E02_VAF08_VAF1_result.RData")

loss1 <- sapply(seq_along(data_Nk100_K3_Q444_E02_VAF08_VAF1_result), function(anom) tail(data_Nk100_K3_Q444_E02_VAF08_VAF1_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk100_K3_Q444_E02_VAF08_VAF1_result[[which.min(loss1)]]
data_Nk100_K3_Q444_E02_VAF08_VAF1_ARI <- adjustedRandIndex(data_Nk100_K3_Q444_E02_VAF08$P, optimal$p)
```

use vaf = 0.8

```{r}
data_Nk100_K3_Q444_E02_VAF08_VAF08_result <- ClusterwiseJICA_varyQ(X = data_Nk100_K3_Q444_E02_VAF08$Xe,  k = 3, nc = c(4,4,4), useInputQ = T, starts = 20, scale = T, VAF = 0.8)
save(data_Nk100_K3_Q444_E02_VAF08_VAF08_result, file = "./data/data_Nk100_K3_Q444_E02_VAF08_VAF08_result.RData")

loss1 <- sapply(seq_along(data_Nk100_K3_Q444_E02_VAF08_VAF08_result), function(anom) tail(data_Nk100_K3_Q444_E02_VAF08_VAF08_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk100_K3_Q444_E02_VAF08_VAF08_result[[which.min(loss1)]]
data_Nk100_K3_Q444_E02_VAF08_VAF08_ARI <- adjustedRandIndex(data_Nk100_K3_Q444_E02_VAF08$P, optimal$p)
```

```{r}
values <- c(data_Nk100_K3_Q444_E02_VAF08_VAF1_ARI, data_Nk100_K3_Q444_E02_VAF08_VAF08_ARI)
names(values) <- c("vaf1ARI", "vaf08ARI")
print(values)
```

### vaf = 1, unequal Q

1.bad model

```{r}
set.seed(123)
data_Nk50_K5_Q44566_E04_VAF1 <- Simulate_CJICA(Nk = 50, Vm = 2500, K = 5, Qvect = c(4,4,5,6,6), E = .4, M = 2, type = 1, cor = .05, VAF = 1)
save(data_Nk50_K5_Q44566_E04_VAF1, file = "./data/data_Nk50_K5_Q44566_E04_VAF1.RData")
```

use input Q and nc will not change

```{r}
load("./data/data_Nk50_K5_Q44566_E04_VAF1.RData")

data_Nk50_K5_Q44566_E04_VAF1_useQ_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q44566_E04_VAF1$Xe, k = 5, nc = c(4,4,5,6,6), useInputQ = T, starts = 20, scale = T, VAF = 1)
save(data_Nk50_K5_Q44566_E04_VAF1_useQ_result, file = "./data/data_Nk50_K5_Q44566_E04_VAF1_useQ_result.RData")

loss1 <- sapply(seq_along(data_Nk50_K5_Q44566_E04_VAF1_useQ_result), function(anom) tail(data_Nk50_K5_Q44566_E04_VAF1_useQ_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk50_K5_Q44566_E04_VAF1_useQ_result[[which.min(loss1)]]
data_Nk50_K5_Q44566_E04_VAF1_useQ_result_ARI <- adjustedRandIndex(data_Nk50_K5_Q44566_E04_VAF1$P, optimal$p)
```

use vaf = 0.8

```{r}
load("./data/data_Nk50_K5_Q44566_E04_VAF1.RData")

data_Nk50_K5_Q44566_E04_VAF1_VAF08_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q44566_E04_VAF1$Xe, k = 5, useInputQ = F, starts = 20, scale = T, VAF = 0.8)
save(data_Nk50_K5_Q44566_E04_VAF1_VAF08_result, file = "./data/data_Nk50_K5_Q44566_E04_VAF1_VAF08_result.RData")

loss1 <- sapply(seq_along(data_Nk50_K5_Q44566_E04_VAF1_VAF08_result), function(anom) tail(data_Nk50_K5_Q44566_E04_VAF1_VAF08_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk50_K5_Q44566_E04_VAF1_VAF08_result[[which.min(loss1)]]
data_Nk50_K5_Q44566_E04_VAF1_VAF08_result_ARI <- adjustedRandIndex(data_Nk50_K5_Q44566_E04_VAF1$P, optimal$p)
```

```{r}
values <- c(data_Nk50_K5_Q44566_E04_VAF1_useQ_result_ARI, data_Nk50_K5_Q44566_E04_VAF1_VAF08_result_ARI)
names(values) <- c("useQARI", "vaf08ARI")
print(values)
```

2.good model

```{r}
set.seed(123)
data_Nk100_K3_Q234_E02_VAF1 <- Simulate_CJICA(Nk = 100, Vm = 2500, K = 3, Qvect = c(2,3,4), E = .2, M = 2, type = 1, cor = .05, VAF = 1)
save(data_Nk100_K3_Q234_E02_VAF1, file = "./data/data_Nk100_K3_Q234_E02_VAF1.RData")
```

use input Q and nc will not change

```{r}
load("./data/data_Nk100_K3_Q234_E02_VAF1.RData")
data_Nk100_K3_Q234_E02_VAF1_useQ_result <- ClusterwiseJICA_varyQ(X = data_Nk100_K3_Q234_E02_VAF1$Xe, k = 3, nc = c(2,3,4), useInputQ = T, starts = 20, scale = T)
save(data_Nk100_K3_Q234_E02_VAF1_useQ_result, file = "./data/data_Nk100_K3_Q234_E02_VAF1_useQ_result.RData")

loss2 <- sapply(seq_along(data_Nk100_K3_Q234_E02_VAF1_useQ_result), function(anom) tail(data_Nk100_K3_Q234_E02_VAF1_useQ_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk100_K3_Q234_E02_VAF1_useQ_result[[which.min(loss2)]]
data_Nk100_K3_Q234_E02_VAF1_useQ_result_ARI <- adjustedRandIndex(data_Nk100_K3_Q234_E02_VAF1$P, optimal$p)
```

use vaf = 0.8

```{r}
data_Nk100_K3_Q234_E02_VAF1_VAF08_result <- ClusterwiseJICA_varyQ(X = data_Nk100_K3_Q234_E02_VAF1$Xe, k = 3, useInputQ = F, starts = 20, scale = T)
save(data_Nk100_K3_Q234_E02_VAF1_VAF08_result, file = "./data/data_Nk100_K3_Q234_E02_VAF1_VAF08_result.RData")

loss2 <- sapply(seq_along(data_Nk100_K3_Q234_E02_VAF1_VAF08_result), function(anom) tail(data_Nk100_K3_Q234_E02_VAF1_VAF08_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk100_K3_Q234_E02_VAF1_VAF08_result[[which.min(loss2)]]
data_Nk100_K3_Q234_E02_VAF1_VAF08_result_ARI <- adjustedRandIndex(data_Nk100_K3_Q234_E02_VAF1$P, optimal$p)
```

```{r}
values <- c(data_Nk100_K3_Q234_E02_VAF1_useQ_result_ARI, data_Nk100_K3_Q234_E02_VAF1_VAF08_result_ARI)
names(values) <- c("useQARI", "vaf08ARI")
print(values)
```

### vaf = 0.8, unequal Q

1.bad model

```{r}
source("./functions/data_simulation_functions.R")
set.seed(123)
data_Nk50_K5_Q44566_E04_VAF08 <- Simulate_CJICA(Nk = 50, Vm = 2500, K = 5, Qvect = c(4,4,5,6,6), E = .4, M = 2, type = 1, cor = .05, VAF = 0.8)
save(data_Nk50_K5_Q44566_E04_VAF08, file = "./data/data_Nk50_K5_Q44566_E04_VAF08.RData")
```

use input Q and nc will not change

```{r}
load("./data/data_Nk50_K5_Q44566_E04_VAF08.RData")
data_Nk50_K5_Q44566_E04_VAF08_useQ_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q44566_E04_VAF08$Xe, k = 5, nc = c(4,4,5,6,6), useInputQ = T, starts = 20, scale = T)
save(data_Nk50_K5_Q44566_E04_VAF08_useQ_result, file = "./data/data_Nk50_K5_Q44566_E04_VAF08_useQ_result.RData")

load("./data/data_Nk50_K5_Q44566_E04_VAF08_useQ_result.RData")
loss1 <- sapply(seq_along(data_Nk50_K5_Q44566_E04_VAF08_useQ_result), function(anom) tail(data_Nk50_K5_Q44566_E04_VAF08_useQ_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk50_K5_Q44566_E04_VAF08_useQ_result[[which.min(loss1)]]
data_Nk50_K5_Q44566_E04_VAF08_useQ_result_ARI <- adjustedRandIndex(data_Nk50_K5_Q44566_E04_VAF08$P, optimal$p)
```

use vaf = 0.8

```{r}
data_Nk50_K5_Q44566_E04_VAF08_VAF08_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q44566_E04_VAF08$Xe, k = 5, useInputQ = F, starts = 20, scale = T, VAF = 0.8)
save(data_Nk50_K5_Q44566_E04_VAF08_VAF08_result, file = "./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_result.RData")

load("./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_result.RData")
loss1 <- sapply(seq_along(data_Nk50_K5_Q44566_E04_VAF08_VAF08_result), function(anom) tail(data_Nk50_K5_Q44566_E04_VAF08_VAF08_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk50_K5_Q44566_E04_VAF08_VAF08_result[[which.min(loss1)]]
data_Nk50_K5_Q44566_E04_VAF08_VAF08_result_ARI <- adjustedRandIndex(data_Nk50_K5_Q44566_E04_VAF08$P, optimal$p)
```

```{r}
values <- c(data_Nk50_K5_Q44566_E04_VAF08_useQ_result_ARI, data_Nk50_K5_Q44566_E04_VAF08_VAF08_result_ARI)
names(values) <- c("useQARI", "vaf08ARI")
print(values)
```

2.good model

```{r}
set.seed(123)
data_Nk100_K3_Q234_E02_VAF08 <- Simulate_CJICA(Nk = 100, Vm = 2500, K = 3, Qvect = c(2,3,4), E = .2, M = 2, type = 1, cor = .05, VAF = 0.8)
save(data_Nk100_K3_Q234_E02_VAF08, file = "./data/data_Nk100_K3_Q234_E02_VAF08.RData")
```

use input Q and nc will not change

```{r}
load("./data/data_Nk100_K3_Q234_E02_VAF08.RData")
data_Nk100_K3_Q234_E02_VAF08_useQ_result <- ClusterwiseJICA_varyQ(X = data_Nk100_K3_Q234_E02_VAF08$Xe, k = 3, nc = c(2,3,4), useInputQ = T, starts = 20, scale = T)
save(data_Nk100_K3_Q234_E02_VAF08_useQ_result, file = "./data/data_Nk100_K3_Q234_E02_VAF08_useQ_result.RData")

load("./data/data_Nk100_K3_Q234_E02_VAF08_useQ_result.RData")
loss1 <- sapply(seq_along(data_Nk100_K3_Q234_E02_VAF08_useQ_result), function(anom) tail(data_Nk100_K3_Q234_E02_VAF08_useQ_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk100_K3_Q234_E02_VAF08_useQ_result[[which.min(loss1)]]
data_Nk100_K3_Q234_E02_VAF08_useQ_result_ARI <- adjustedRandIndex(data_Nk100_K3_Q234_E02_VAF08$P, optimal$p)
```

use vaf = 0.8

```{r}
load("./data/data_Nk100_K3_Q234_E02_VAF08.RData")
data_Nk100_K3_Q234_E02_VAF08_VAF08_result <- ClusterwiseJICA_varyQ(X = data_Nk100_K3_Q234_E02_VAF08$Xe,  k = 3, useInputQ = F, starts = 20, scale = T, VAF = 0.8)
save(data_Nk100_K3_Q234_E02_VAF08_VAF08_result, file = "./data/data_Nk100_K3_Q234_E02_VAF08_VAF08_result.RData")

loss1 <- sapply(seq_along(data_Nk100_K3_Q234_E02_VAF08_VAF08_result), function(anom) tail(data_Nk100_K3_Q234_E02_VAF08_VAF08_result[[anom]]$lossiter, n = 1))
optimal <- data_Nk100_K3_Q234_E02_VAF08_VAF08_result[[which.min(loss1)]]
data_Nk100_K3_Q234_E02_VAF08_VAF08_result_ARI <- adjustedRandIndex(data_Nk100_K3_Q234_E02_VAF08$P, optimal$p)
```

```{r}
values <- c(data_Nk100_K3_Q234_E02_VAF08_useQ_result_ARI, data_Nk100_K3_Q234_E02_VAF08_VAF08_result_ARI)
names(values) <- c("useQARI", "vaf08ARI")
print(values)
```

## 6. test penalty

### vaf = 0.8, unequal Q

1.bad model

```{r}
load("./data/data_Nk50_K5_Q44566_E04_VAF08.RData")
```

complexity = 1

```{r}

data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp1_chull_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q44566_E04_VAF08$Xe, k = 5, useInputQ = F, starts = 20, scale = F, VAF = 0.8, complexity = 1, useChull = T)
save(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp1_chull_result, file = "./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp1_chull_result.RData")

```

```{r}
load("./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp1_chull_result.RData")
aic_sums <- sapply(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp1_chull_result, function(res) res$Lir$aicSum)
min_index <- which.min(aic_sums)
optimal <- data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp1_chull_result[[min_index]]
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp1_chull_result_ARI <- adjustedRandIndex(
  data_Nk50_K5_Q44566_E04_VAF08$P, 
  optimal$p
)
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp1_chull_result_ARI
```

complexity = 2

```{r}

data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp2_chull_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q44566_E04_VAF08$Xe, k = 5, useInputQ = F, starts = 20, scale = F, VAF = 0.8, complex = 2, useChull = T, Vm = 2500)
save(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp2_chull_result, file = "./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp2_chull_result.RData")

```

```{r}
load("./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp2_chull_result.RData")
aic_sums <- sapply(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp2_chull_result, function(res) res$Lir$aicSum)
min_index <- which.min(aic_sums)
optimal <- data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp2_chull_result[[min_index]]
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp2_chull_result_ARI <- adjustedRandIndex(
  data_Nk50_K5_Q44566_E04_VAF08$P, 
  optimal$p
)
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp2_chull_result_ARI
```

complexity = 3

```{r}

data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp3_chull_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q44566_E04_VAF08$Xe, , k = 5, useInputQ = F, starts = 20, scale = F, VAF = 0.8, complex = 3, useChull = T, Vm = 2500)
save(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp3_chull_result, file = "./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp3_chull_result.RData")

```

```{r}
load("./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp3_chull_result.RData")
aic_sums <- sapply(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp3_chull_result, function(res) res$Lir$aicSum)
min_index <- which.min(aic_sums)
optimal <- data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp3_chull_result[[min_index]]
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp3_chull_result_ARI <- adjustedRandIndex(
  data_Nk50_K5_Q44566_E04_VAF08$P, 
  optimal$p
)
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp3_chull_result_ARI
```

complexity = 4

```{r}

data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp4_chull_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q44566_E04_VAF08$Xe, k = 5, useInputQ = F, starts = 20, scale = F, VAF = 0.8, complex = 4, Vm = 2500, useChull = T)
save(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp4_chull_result, file = "./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp4_chull_result.RData")

```

```{r}
load("./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp4_chull_result.RData")
aic_sums <- sapply(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp4_chull_result, function(res) res$Lir$aicSum)
min_index <- which.min(aic_sums)
optimal <- data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp4_chull_result[[min_index]]
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp4_chull_result_ARI <- adjustedRandIndex(
  data_Nk50_K5_Q44566_E04_VAF08$P, 
  optimal$p
)
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp4_chull_result_ARI
```

complexity = 5

```{r}

data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp5_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q44566_E04_VAF08$Xe, k = 5, useInputQ = F, starts = 20, scale = F, VAF = 0.8, complexity = 5)
save(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp5_result, file = "./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp5_result.RData")

```

```{r}
load("./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp5_result.RData")
aic_sums <- sapply(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp5_result, function(res) res$Lir$aicSum)
min_index <- which.min(aic_sums)
optimal <- data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp5_result[[min_index]]
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp5_result_ARI <- adjustedRandIndex(
  data_Nk50_K5_Q44566_E04_VAF08$P, 
  optimal$p
)
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp5_result_ARI
```

complexity = 6

```{r}

data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp6_chull_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q44566_E04_VAF08$Xe, k = 5, useInputQ = F, starts = 20, scale = F, VAF = 0.8, complex = 6, Vm = 2500, useChull = T)
save(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp6_chull_result, file = "./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp6_chull_result.RData")

```

```{r}
load("./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp6_chull_result.RData")
aic_sums <- sapply(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp6_chull_result, function(res) res$Lir$aicSum)
min_index <- which.min(aic_sums)
optimal <- data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp6_chull_result[[min_index]]
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp6_chull_result_ARI <- adjustedRandIndex(
  data_Nk50_K5_Q44566_E04_VAF08$P, 
  optimal$p
)
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp6_chull_result_ARI
```

complexity = 7

```{r}

data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp7_chull_result <- ClusterwiseJICA_varyQ(X = data_Nk50_K5_Q44566_E04_VAF08$Xe, k = 5, useInputQ = F, starts = 20, scale = F, VAF = 0.8, complex = 7, Vm = 2500, useChull = T)
save(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp7_chull_result, file = "./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp7_chull_result.RData")

```

```{r}
load("./data/data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp7_chull_result.RData")
aic_sums <- sapply(data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp7_chull_result, function(res) res$Lir$aicSum)
min_index <- which.min(aic_sums)
optimal <- data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp7_chull_result[[min_index]]
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp7_chull_result_ARI <- adjustedRandIndex(
  data_Nk50_K5_Q44566_E04_VAF08$P, 
  optimal$p
)
data_Nk50_K5_Q44566_E04_VAF08_VAF08_comp7_chull_result_ARI
```

```{r}
complexity.fit <- cbind(c(305,456,460,607),
c(152,89,79,71))
output <- CHull(complexity.fit)
plot(output)
print(output)
summary(output)
```
